---
title: "Assigment - kNN_hcv"
author: "Ha Trang Nguyen"
review: "Ngoc Minh Nguyen"
 
date: "17/09/2022"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---
## Setting up
Loading datasets into scripts


```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
```

------------------------------------------------------------------------

## A. Business understanding
The data set contains different laboratory values of blood donors, Hepatitis C, Fibrosis, Cirrhosis patients and their demographic values such as age and sex. This model objective is to analyze the dataset of people to define their blood characteristics and whether that person is able to donate blood or not.

## B. Data Understanding
### Read data
```{r}
#Read from url
url1 <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/KNN-hcvdat0.csv"
rawDF1 <- read_csv(url1)
str(rawDF1)
View(rawDF1)
```

## C. Data Preparation
### 1. Cleaning data
```{r}
#Randomize the data to avoid biases or data that is not spread evenly 
cleanDF <- rawDF1[sample(1:nrow(rawDF1)),]
#View data
View(cleanDF)
#Eliminate the first column which is unique for each variable 
cleanDF <- cleanDF[-1]
#Check the labels after the elimination 
head(cleanDF) 

#Counting and proportion among categories
cntDiag <- table(cleanDF$Category)
propCat <- round(prop.table(cntDiag) * 100 , digits = 1)

cntDiag
propCat
```


### 2. Setting labels for categories
 
```{r}
cleanDF$Category <- factor(cleanDF$Category, levels = c("0=Blood Donor", "0s=suspect Blood Donor", "1=Hepatitis", "2=Fibrosis", "3=Cirrhosis"), labels = c("Able to donate blood", "Not able to donate blood","Hepatitis","Fibrosis","Cirrhosis")) %>% relevel("Not able to donate blood")
head(cleanDF, 10)
```
### 3. Calculating proportion after labeling categories
```{r}
cntDiag_new <- table(cleanDF$Category)
propCat_new <- round(prop.table(cntDiag2) * 100 , digits = 1)

cntDiag_new  
propCat_new
```

### 3. Analyzing and checking variables
```{r}
summary(cleanDF[c("ALB", "ALP", "ALT", "AST", "BIL", "CHE", "CHOL", "CREA", "GGT", "PROT")])
```

Checking for missing values and replacing them in dataset

```{r}
sum(is.na(cleanDF))
#=31 
cleanDF[is.na(cleanDF)] <- 0

summary(cleanDF[c("ALB", "ALP", "ALT", "AST", "BIL", "CHE", "CHOL", "CREA", "GGT", "PROT")])
```

### 4. Normalizing features

Setting a function of normalization
```{r}
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))}
```


Testing the function 
```{r}
nCols <- dim(cleanDF)[2]
cleanDF_n <- sapply(4:nCols,
                    function(x) {
  normalize(cleanDF[,x])
}) %>% as.data.frame()

summary(cleanDF_n[c("ALB", "ALP", "ALT", "AST", "BIL", "CHE", "CHOL", "CREA", "GGT", "PROT")])
```
### 5. Test sets and train sets

```{r}
trainDF_feat <- cleanDF_n[1:515,  ]
testDF_feat <- cleanDF_n[516:615,  ]

trainDF_labels <- cleanDF[1:515,  1]
testDF_labels <- cleanDF[516:615,  1]
```

## D. Modeling
```{r}
cleanDF_test_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = 15)
head(cleanDF_test_pred)
confusionMatrix(cleanDF_test_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))
```

## E. Evaluation and Deployment




reviewer adds suggestions for improving the model
